Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-05-12 response.tex

\section{Comparison with other works}

From the reviewer:

\begin{quote}
  It is not clear why References 4 and 5 were chosen as the only reference points.
  I suspect it is because they were also measured at 1420 MHz and during a solar eclipse. If this is the case, it should be stated.
\end{quote}

\noindent We have included the following to the theoretical lightcurve comparison section:

@@

\begin{quote}
  \input{sections/comparison_sources.tex}
\end{quote}

\begin{quote}
  The authors should also consider comparing it to the long history of measurements of solar radii at radio wavelengths through other methods, such as those listed in Menezes \& Valio (2018).
  Does this measurement fit the general trend of radius with frequency?
\end{quote}

\noindent We have added the following to our comparision with other works:

\begin{quote}
  \input{sections/history.tex}
\end{quote}

\section{Emission source}

\begin{quote}
  Finally, indicate, perhaps in the introduction or discussion, what kind of emission IS being given off in the radio that gives us this larger radius? (It’s not from the blackbody spectrum that dominates in the visible.)
\end{quote}

### 2025-05-12 sections/introduction.tex
Adding an explanation of the emission mechanism

Our goal with this project is to determine the size of the sun in the radio frequency by using observations during the April 8th, 2024 total solar eclipse.
Our radio telescope is specifically focused on the electron spin-flip transition of Hydrogen, which is observed at 1420MHz.
We collected data in both the optical and radio frequencies, providing a unique opportunity to compare the relative size in the optical and radio spectra.
To accomplish this, we need to determine how much of the solar disk is obscured by the moon during totality in both the optical and radio wavelengths.
We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
In order to compare the radio eclipse to the optical eclipse, we have two sources of optical lightcurve data: a livestream from the UCA Observatory and a broad-spectrum light sensor pointed at the sky.
We also generated theoretical lightcurves using the software \texttt{Stellarium}\cite{zotti_simulated_2020} and the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.
Using this data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.

>>>>

Our goal with this project is to determine the size of the sun in the radio frequency by using observations during the April 8th, 2024 total solar eclipse.
Our radio telescope is specifically focused on the electron spin-flip transition of Hydrogen, which is observed at 1420MHz.
\input{sections/emission.tex}
We collected data in both the optical and radio frequencies, providing a unique opportunity to compare the relative size in the optical and radio spectra.
To accomplish this, we need to determine how much of the solar disk is obscured by the moon during totality in both the optical and radio wavelengths.
We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
In order to compare the radio eclipse to the optical eclipse, we have two sources of optical lightcurve data: a livestream from the UCA Observatory and a broad-spectrum light sensor pointed at the sky.
We also generated theoretical lightcurves using the software \texttt{Stellarium}\cite{zotti_simulated_2020} and the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.
Using these data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.
